Miniproject - Algebraic Geometry

### 2021-12-13 Algebraic geometry/submission.tex
added rust syntax highlighting to combinatorics

    Have $a_1 b_4 = a_4 b_1$ and $a_2 b_4 = a_4 b_2$.
    We know that $a_1 b_4 \neq 0$ and so
    \begin{equation*}
        \frac {a_2} {a_1} = \frac {a_2 b_4} {a_1 b_4} = \frac {a_4 b_2} {a_4 b_1} = \frac {b_2} {b_1} \ \Rightarrow \ a_2 b_1 = a_1 b_2
    \end{equation*}
    This contradicts $a_1 b_2 - a_2 b_1 = 1$.
\end{proof}

\begin{lemma}
    \label{prop:linear_transform_extpow}
    Let $A = (a_{ij}) \in \GL_d(k)$ and $v_1, ..., v_d \in V$.
    Then
    \begin{equation*}
        \Bigl( \sum_j a_{1j}v_j \Bigl) \wedge ... \wedge \Bigl( \sum_{j} a_{dj} v_j \Bigr) = \det(A) (v_1 \wedge ... \wedge v_d)
    \end{equation*}
\end{lemma}
\begin{proof}
    By a direct computation using Lemma~\ref{prop:basic_properties_exterior_product}, we find
    \begin{align*}
        &\Bigl( \sum_j a_{ij} v_j \Bigr) \wedge ... \wedge \Bigl( \sum_j a_{dj} v_j \Bigr) = \sum_{j_1, ..., j_d} a_{1j_1} ... a_{dj_d} (v_{j_1} \wedge ... \wedge v_{j_d}) \\
        = &\sum_{\pi \in S_d} a_{1\pi(1)} ... a_{d\pi(d)} (v_{\pi(1)} \wedge ... \wedge v_{\pi(d)}) \\
        = &\sum_{\pi \in S_d} a_{1\pi(1)} ... a_{d\pi(d)} \sgn(\pi) (v_1 \wedge ... \wedge v_d) \\
        = &(v_1 \wedge ... \wedge v_d) \ \sum_{\pi \in S_d} \sgn(\pi) \prod_{j = 1}^d a_{j\pi(j)} = \det(A) (v_1 \wedge ... \wedge v_d)
    \end{align*}
    where the last equality holds due to the Leibniz determinant formula.
\end{proof}
The next two lemmas are quite fundamental, as they can be used as a basic tool to prove linear independence in the exterior product.
\begin{lemma}
    \label{prop:basis_product_independence}
    The vectors $b_{i_1} \wedge ... \wedge b_{i_d}$ for $i_1 < ... < i_d$ form a basis of $\extpow^d V$.
\end{lemma}
\begin{proof}
    This proof is slightly technical, as I wanted to provide a rigorous proof using only the definition of $\extpow^d V$ and some properties of the symmetric group $S_d$.
    The core idea is to show the linear independence by going to down to the free product underlying $\extpow^d V$, and then show that we cannot use the vectors $(b_{i_1}, ..., b_{i_d}) + (b_{i_1}, ..., b_{i_{j + 1}}, b_{i_j}, ..., i_d)$ to create a nontrivial linear combination.
    Namely, assuming we have such a nontrivial linear combination, we can group it into the part where the order of the $i_1, ..., i_d$ has even/odd parity.
    The vectors with $i_1 < ... < i_d$ clearly are all on one side, and from this we can derive the claim.

@@

    For the other direction, let $v_1, ..., v_d$ be linearly independent.
    Clearly, we can extend them to a basis $v_1, ..., v_n$ of $V$.
    We then see that there is a matrix $A = (a_{ij}) \in \GL_n(k)$ with $v_i = \sum_j a_{ij} b_j$.
    So by Lemma~\ref{prop:linear_transform_extpow} have
    \begin{equation*}
        v_1 \wedge ... \wedge v_n = \underbrace{\det(A)}_{\neq 0} (b_1 \wedge ... \wedge b_n) \neq 0
    \end{equation*}
    So clearly $v_1 \wedge ... \wedge v_d \neq 0$ as $0 \wedge (v_{d + 1} \wedge ... \wedge v_n) = 0$ for all $v_{d + 1}, ..., v_n \in V$.
\end{proof}

\begin{lemma}[Question (c)]
    \label{prop:characterization_decomposable_d_even}
    Let $d$ be even.
    An element $\omega \in \extpow^d V$ is decomposable if and only if $\omega \wedge \omega \in \extpow^{2d} V$ is zero.
\end{lemma}
\begin{proof}
    The direction $\Rightarrow$ even holds generally. Assume $\omega = v_1 \wedge ... \wedge v_d$.
    Then
    \begin{equation*}
        \omega \wedge \omega = v_1 \wedge ... \wedge v_d \wedge v_1 \wedge ... \wedge v_d = 0
    \end{equation*}
    by Lemma~\ref{prop:basic_properties_exterior_product}. 
    The other direction is more interesting.

@@

In this part, we want to consider the connection of exterior powers to the Grassmanian.
\begin{remark}[Question (a)]
    First of all, assume there are two bases $v_1, ..., v_d$ and $u_1, ..., u_d$ of a $d$-dimensional vector space $U$. 
    Then there exists a basis change matrix $A = (a_{ij}) \in \GL_d(k)$ with
    \begin{equation*}
        u_i = \sum_j a_{ij} v_j
    \end{equation*}
    So by Lemma~\ref{prop:linear_transform_extpow}, it follows that
    \begin{equation*}
        u_1 \wedge ... \wedge u_d = \det(A) (v_1 \wedge ... \wedge v_d)
    \end{equation*}
    As $v_1, ..., v_d$ resp. $u_1, ..., u_d$ are bases, they are linearly independent and in particular, we see that
    \begin{equation*}
        v_1 \wedge ... \wedge v_d \neq 0 \quad \text{and} \quad u_1 \wedge ... \wedge u_d \neq 0
    \end{equation*}
    by Lemma~\ref{prop:extpow_zero_iff_independent}.
    Hence they have well-defined images $[v_1 \wedge ... \wedge v_d]$ resp. $[u_1 \wedge ... \wedge u_d]$ in the projective space $\Proj(\extpow^d V)$.
    By the above, find
    \begin{equation*}
        [v_1 \wedge ... \wedge v_d] = [u_1 \wedge ... \wedge u_d]
    \end{equation*}
\end{remark}
This allows us to study the Grassmanian $\Gr(d, V)$ of a fixed vector space $V$.
\begin{definition}
    Define the map
    \begin{equation*}
        \phi: \Gr(d, V) \to \Proj(\extpow^d V), \quad \vspan\{v_1, ..., v_d\} \mapsto [v_1 \wedge ... \wedge v_d]
    \end{equation*}
    which is well-defined by Lemma~\ref{prop:linear_transform_extpow} as described above.
\end{definition}
\begin{lemma}[1a]
    We have
    \begin{equation*}
        \mathrm{im}\phi = D := \{ [v] \in \Proj(\extpow^d V) \ | \ \text{$v$ decomposable}\}
    \end{equation*}
\end{lemma}
\begin{proof}
    First of all, note that the set $D$ is well-defined, as $v$ is decomposable if and only if $\lambda v$ is decomposable, for all $\lambda \in k^*$.

@@

    \begin{align*}
        \det(A_I(v_1, ..., v_i + v'_i, ..., v_d)) = \det(A_I(v_1, ..., v_d)) + \det(A_I(v_1, ..., v'_i, ..., v_d))
    \end{align*}
    and
    \begin{align*}
        \det(A_I(v_1, ..., \lambda v_i, ..., v_d)) = \lambda\det(A_I(v_1, ..., v_d))
    \end{align*}
    and
    \begin{equation*}
        \det(A_I(v_1, ..., v_{j + 1}, v_j, ..., v_d)) = -\det(A_I(v_1, ..., v_d))
    \end{equation*}
    However, these properties follow from the well-known properties of the determinant.
    In particular, $\det$ is linear in each column and swapping columns negates the determinant.
    It follows that $f$ is indeed well-defined.

    It is clear by definition that $f$ is linear, so it is left to show that it is bijective. 
    To show surjectivity, note that the $\pm e_I, I \in \{1, ..., n\}^{(d)}$ form a basis of $k^{\{1, ..., n\}^{(d)}}$.
    Clearly for $I = \{i_1, ..., i_d\}, J \in \{1, ..., n\}^{(d)}$ we have that
    \begin{equation*}
        f(e_{i_1} \wedge ... \wedge e_{i_d})_J = \det(A_J(e_{i_1}, ..., e_{i_j})) = \begin{cases}
            0 & \text{if $J \not\subseteq I$} \\
            \pm 1 & \text{if $J \subseteq I$}
        \end{cases}
    \end{equation*}
    so $f(e_{i_1} \wedge ... \wedge e_{i_d}) = e_I$ and we deduce that $\mathrm{im}f = \Proj^{\{1, ..., k\}^{(d)}}$.

    Finally, note that
    \begin{equation*}
        e_{i_1} \wedge ... \wedge e_{i_d}
    \end{equation*}
    for $i_1 < ... < i_d$ form a basis of $\extpow^d k^n$.
    Clearly, they span $\extpow^d k^n$, and the following argument shows that they are linearly independent.
    Assume
    \begin{equation*}
        \sum_{i_1 < ... < i_d} \lambda_{i_1, ..., i_d} (e_{i_1} \wedge ... \wedge e_{i_d}) = 0
    \end{equation*}
    Then
    \begin{equation*}
        0 = e_1 \wedge \Bigl( \sum_{1 < i_2 < ... < i_d} \lambda_{1, i_2, ..., i_d} (e_{i_2} \wedge .. \wedge e_{i_d}) \Bigr) + \sum_{1 < i_1 < ... < i_d} \lambda_{i_1, ..., i_d} (e_{i_1} \wedge ... \wedge e_{i_d} )
    \end{equation*}
    Clearly $e_1 \notin \vspan\{e_2, ..., e_n\}$ and so by Lemma~\ref{prop:subspace_closed} we see that
    \begin{equation*}
        \sum_{1 < i_2 < ... < i_d} \lambda_{1, i_2, ..., i_d} (e_{i_2} \wedge ... \wedge e_{i_d}) = 0
    \end{equation*}
    Repeating this argument inductively shows that $\lambda_{1, 2, ..., d} = 0$.
    As $k^n$ is symmetric w.r.t. permuting the $e_j$, we see that all $\lambda_{i_1, ..., i_d} = 0$ are zero.

    It follows that $\dim(\extpow^d k^n) = \dim(\Proj^{\{1, ..., n\}^{(d)}})$ and we find that $f$ is also injective.
\end{proof}
\begin{corollary}[Question (b)]
    \label{prop:image_phi}
    Let $\bar{f}: \Proj(\extpow^d k^n) \to \Proj^{{n \choose d} - 1}$ be the map $f$ from before modulo $k^*$.
    Then
    \begin{equation*}
        \rho = \bar{f} \circ \phi
    \end{equation*}
    and in particular, we see that $\phi(Gr(d, n))$ is a projective variety and isomorphic to $\rho(\Gr(d, n))$.
\end{corollary}
\begin{proposition}[Question (c)]
    The map $\phi$ is injective.
\end{proposition}
\begin{proof}
    Consider two $d$-dimensional subspaces $U, W$ of $k^n$ with $\phi(U) = \phi(W)$.
    Let $u_1, ..., u_l$ be a basis of $U \cap W$ and extend it to bases $u_1, ..., u_d$ of $U$ and $u_1, ..., u_l, w_{l + 1}, ..., w_d$ of $W$.
    As $\phi(U) = \phi(W)$, we can assume that the $u_i, w_i$ are scaled such that
    \begin{align*}
        0 =& (u_1 \wedge ... \wedge u_d) - (u_1 \wedge ... \wedge u_l \wedge w_{l + 1} \wedge ... \wedge w_d) \\
        =& u_1 \wedge ... \wedge u_l \wedge \bigl( (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) \bigr)
    \end{align*}
    By Lemma~\ref{prop:subspace_closed} we see that
    \begin{equation*}
        u_2 \wedge ... \wedge u_l \wedge \bigl( (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) \bigr) = 0
    \end{equation*}
    as $u_1 \notin \vspan\{u_2, ..., u_d, w_{l + 1}, ..., w_d\}$.
    Inductively, this argument shows that
    \begin{equation*}
        (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) = 0
    \end{equation*}
    If $l < d$, we can now apply Lemma~\ref{prop:subspace_closed} again to see that
    \begin{equation*}
        u_{l + 1} \in \vspan\{ u_{l + 2}, ..., u_d, w_{l + 1}, ..., w_d \}
    \end{equation*}
    as $u_{l + 2} \wedge ... \wedge u_d \neq 0$ by Lemma~\ref{prop:extpow_zero_iff_independent}.
    However, this contradicts the linear independence of $u_{l + 1}, ..., u_d, w_{l + 1}, ..., w_d$.
    Hence it must be $l = d$ and so $U = W$.
\end{proof}

@@

First of all, we introduce coordinates on $\Proj(\extpow^d k^n)$.

@@

    Note that in the proof of Lemma~\ref{prop:isomorphism_extpow_det} it was shown that $v_{i_1} \wedge ... \wedge v_{i_d}$ for $i_1 < ... < i_d$ is a basis of $\extpow^d k^n$ if $v_1, ..., v_n$ is a basis of $V$.

@@

        \omega \in \mathrm{im}\phi \ \Leftrightarrow \ \omega \wedge \omega = 0

@@

    In $\Proj(\extpow^d V)$ we find that

@@

    Changing the indices used for the coordinates, we find
        \Gr(2, 4) = \V(x_0 x_5 + x_2 x_3 - x_2 x_4)

@@

    Then for an ideal $I \leq R$ have that the monomials $x_0^{\alpha_0} ... x_n^{\alpha_n} \notin \mathrm{lt}(I)$ are a $k$-vector space basis of $R/I$.

@@

    Consider homogeneous polynomials $f_{i, j, u, v} \in R$ and
    \begin{equation*}
        F = \sum_{i < j < u < v} f_{i, j, u, v} \ (x_{i, v} x_{j, u} - x_{i, u} x_{j, v} + x_{i, j} x_{u, v})
    \end{equation*}
    We want to show that $\mathrm{lt}(F) \in J$.

@@

    So consider now the second case, i.e. $\mathrm{lt}(F) = \epsilon \ x_{i, u} \ x_{j, v} \ f_{i, j, u, v}$.
    Since $x_{i, v} \ x_{j, u} \ f_{i, j, u, v} \succ x_{i, u} \ x_{j, v} \ f_{i, j, u, v}$, we see that the term $x_{i, v} \ x_{j, u} \ f_{i, j, u, v}$ cannot occur in $F$, i.e. must ``cancel out''.
    Hence the monomial $\epsilon \ x_{i, v} \ x_{j, u} \ f_{i, j, u, v}$ has a nonzero coefficient in
    \begin{equation*}
        F - f_{i, j, u, v} x_{i, v} x_{j, u} = \sum_{\substack{a < b < c < d\\(a, b, c, d) \neq (i, j, u, v)}} f_{a, b, c, d} \ (x_{a, d} x_{b, c} - x_{a, c} x_{b, d} + x_{a, b} x_{c, d})
    \end{equation*}
    and so for $(a, b, c, d) \neq (i, j, u, v), \epsilon' \in k^*$ have that
    \begin{align*}
        f_{i, j, u, v} \ x_{i, v} \ x_{j, u} &= \epsilon' f_{a, b, c, d} \ x_{a, d} \ x_{b, c} \quad \text{or}\\
        f_{i, j, u, v} \ x_{i, v} \ x_{j, u} &= \epsilon' f_{a, b, c, d} \ x_{a, c} \ x_{b, d} \quad \text{or}\\
        f_{i, j, u, v} \ x_{i, v} \ x_{j, u} &= \epsilon' f_{a, b, c, d} \ x_{a, b} \ x_{c, d}
    \end{align*}
    However, the second and third case imply that $f_{a, b, c, d} \ x_{a, d} \ x_{b, c} \succ f_{i, j, u, v} \ x_{i, v} \ x_{j, u}$.
    Hence, the ``new'' monomial $f_{a, b, c, d} \ x_{a, d} \ x_{b, c}$ also has to ``cancel out'' in the sum representation of $F$, as comes after $\mathrm{lt}(F) = \epsilon x_{i, u} \ x_{j, v} \ f_{i, j, u, v}$ in the order $\preceq$.
    So applying the whole argument inductively (induction on the number of monomials $\succ f_{i, j, u, v} \ x_{i, v} \ x_{j, u}$ that occur in any of the polynomials we work with), we end up in the first case
    \footnote{There is a small argument missing here, namely that we apply the next argument on each step of the induction, to show the claim for $f_{i, j, u, v} \ x_{i, v} \ x_{j, u}$. However, it should be easy to see that this is possible.}.

>>>>

    Have $a_1 b_4 = a_4 b_1$ and $a_2 b_4 = a_4 b_2$.
    We know that $a_1 b_4 \neq 0$ and so
    \begin{equation*}
        \frac {a_2} {a_1} = \frac {a_2 b_4} {a_1 b_4} = \frac {a_4 b_2} {a_4 b_1} = \frac {b_2} {b_1} \ \Rightarrow \ a_2 b_1 = a_1 b_2
    \end{equation*}
    This contradicts $a_1 b_2 - a_2 b_1 = 1$.
\end{proof}
For the next parts of the mini project, we first need more basic properties of the exterior product.
\begin{lemma}
    \label{prop:linear_transform_extpow}
    Let $A = (a_{ij}) \in \GL_d(k)$ and $v_1, ..., v_d \in V$.
    Then
    \begin{equation*}
        \Bigl( \sum_j a_{1j}v_j \Bigl) \wedge ... \wedge \Bigl( \sum_{j} a_{dj} v_j \Bigr) = \det(A) (v_1 \wedge ... \wedge v_d)
    \end{equation*}
\end{lemma}
\begin{proof}
    By a direct computation using Lemma~\ref{prop:basic_properties_exterior_product}, we find
    \begin{align*}
        &\Bigl( \sum_j a_{ij} v_j \Bigr) \wedge ... \wedge \Bigl( \sum_j a_{dj} v_j \Bigr) = \sum_{j_1, ..., j_d} a_{1j_1} ... a_{dj_d} (v_{j_1} \wedge ... \wedge v_{j_d}) \\
        = &\sum_{\pi \in S_d} a_{1\pi(1)} ... a_{d\pi(d)} (v_{\pi(1)} \wedge ... \wedge v_{\pi(d)}) \\
        = &\sum_{\pi \in S_d} a_{1\pi(1)} ... a_{d\pi(d)} \sgn(\pi) (v_1 \wedge ... \wedge v_d) \\
        = &(v_1 \wedge ... \wedge v_d) \ \sum_{\pi \in S_d} \sgn(\pi) \prod_{j = 1}^d a_{j\pi(j)} = \det(A) (v_1 \wedge ... \wedge v_d)
    \end{align*}
    where the last equality holds due to the Leibniz determinant formula.
\end{proof}
The next two lemmas are quite fundamental, as they can be used as a basic tool to prove linear independence in the exterior product.
\begin{lemma}
    \label{prop:basis_product_independence}
    The vectors $b_{i_1} \wedge ... \wedge b_{i_d}$ for $i_1 < ... < i_d$ form a basis of $\extpow^d V$.
\end{lemma}
\begin{proof}
    This proof is slightly technical, as I wanted to provide a rigorous proof using only the definition of $\extpow^d V$ and some properties of the symmetric group $S_d$.
    The core idea is to show the linear independence by going to down to the free product underlying $\extpow^d V$, and then show that we cannot use the vectors $(b_{i_1}, ..., b_{i_d}) + (b_{i_1}, ..., b_{i_{j + 1}}, b_{i_j}, ..., i_d)$ to create a nontrivial linear combination.
    Namely, assuming we have such a nontrivial linear combination, we can group it into the part where the order of the $i_1, ..., i_d$ has even/odd parity.
    The vectors with $i_1 < ... < i_d$ clearly are all on one side, and from this we can derive the claim.

@@

    For the other direction, let $v_1, ..., v_d$ be linearly independent.
    Clearly, we can extend them to a basis $v_1, ..., v_n$ of $V$.
    We then see that there is a matrix $A = (a_{ij}) \in \GL_n(k)$ with $v_i = \sum_j a_{ij} b_j$.
    So by Lemma~\ref{prop:linear_transform_extpow} have
    \begin{equation*}
        v_1 \wedge ... \wedge v_n = \underbrace{\det(A)}_{\neq 0} (b_1 \wedge ... \wedge b_n) \neq 0
    \end{equation*}
    So clearly $v_1 \wedge ... \wedge v_d \neq 0$ as $0 \wedge (v_{d + 1} \wedge ... \wedge v_n) = 0$ for all $v_{d + 1}, ..., v_n \in V$.
\end{proof}
Now we can see that in general, the exterior product contains not decomposable elements.
\begin{lemma}[Question (c)]
    \label{prop:characterization_decomposable_d_even}
    Let $d$ be even.
    An element $\omega \in \extpow^d V$ is decomposable if and only if $\omega \wedge \omega \in \extpow^{2d} V$ is zero.
\end{lemma}
\begin{proof}
    The direction $\Rightarrow$ even holds generally. Assume $\omega = v_1 \wedge ... \wedge v_d$.
    Then
    \begin{equation*}
        \omega \wedge \omega = v_1 \wedge ... \wedge v_d \wedge v_1 \wedge ... \wedge v_d = 0
    \end{equation*}
    by Lemma~\ref{prop:basic_properties_exterior_product}. 
    The other direction is more interesting.

@@

In this part, we want to consider the connection of exterior powers to the Grassmanian.
\begin{remark}[Question (a)]
    First of all, assume there are two bases $v_1, ..., v_d$ and $u_1, ..., u_d$ of a $d$-dimensional vector space $U$. 
    Then there exists a basis change matrix $A = (a_{ij}) \in \GL_d(k)$ with
    \begin{equation*}
        u_i = \sum_j a_{ij} v_j
    \end{equation*}
    So by Lemma~\ref{prop:linear_transform_extpow}, it follows that
    \begin{equation*}
        u_1 \wedge ... \wedge u_d = \det(A) (v_1 \wedge ... \wedge v_d)
    \end{equation*}
    As $v_1, ..., v_d$ resp. $u_1, ..., u_d$ are bases, they are linearly independent and in particular, we see that
    \begin{equation*}
        v_1 \wedge ... \wedge v_d \neq 0 \quad \text{and} \quad u_1 \wedge ... \wedge u_d \neq 0
    \end{equation*}
    by Lemma~\ref{prop:extpow_zero_iff_independent}.
    Hence they have well-defined images $[v_1 \wedge ... \wedge v_d]$ resp. $[u_1 \wedge ... \wedge u_d]$ in the projective space $\Proj(\extpow^d V)$.
    By the above, find
    \begin{equation*}
        [v_1 \wedge ... \wedge v_d] = [u_1 \wedge ... \wedge u_d]
    \end{equation*}
\end{remark}
This allows us to study the Grassmanian $\Gr(d, V)$ of a fixed vector space $V$.
\begin{definition}
    Define the map
    \begin{equation*}
        \phi: \Gr(d, V) \to \Proj(\extpow^d V), \quad \vspan\{v_1, ..., v_d\} \mapsto [v_1 \wedge ... \wedge v_d]
    \end{equation*}
    which is well-defined by Lemma~\ref{prop:linear_transform_extpow} as described above.
\end{definition}
\begin{lemma}[Question (a)]
    We have
    \begin{equation*}
        \mathrm{im}\phi = D := \{ [v] \in \Proj(\extpow^d V) \ | \ \text{$v$ decomposable}\}
    \end{equation*}
\end{lemma}
\begin{proof}
    First of all, note that the set $D$ is well-defined, as $v$ is decomposable if and only if $\lambda v$ is decomposable, for all $\lambda \in k^*$.

@@

    It is clear by definition that $f$ is linear, so it is left to show that it is bijective. 
    To show surjectivity, note that the $\pm e_I, I \in \{1, ..., n\}^{(d)}$ form a basis of $k^{\{1, ..., n\}^{(d)}}$.
    Clearly for $I = \{i_1, ..., i_d\}, J \in \{1, ..., n\}^{(d)}$ we have that
    \begin{equation*}
        f(e_{i_1} \wedge ... \wedge e_{i_d})_J = \det(A_J(e_{i_1}, ..., e_{i_j})) = \begin{cases}
            0 & \text{if $J \not\subseteq I$} \\
            \pm 1 & \text{if $J \subseteq I$}
        \end{cases}
    \end{equation*}
    so $f(e_{i_1} \wedge ... \wedge e_{i_d}) = e_I$ and we deduce that $\mathrm{im}f = k^{\{1, ..., k\}^{(d)}}$.

    Finally, note that
    \begin{equation*}
        e_{i_1} \wedge ... \wedge e_{i_d}
    \end{equation*}
    for $i_1 < ... < i_d$ form a basis of $\extpow^d k^n$ by Lemma~\ref{prop:basis_product_independence}.
    It follows that $\dim(\extpow^d k^n) = \dim(\Proj^{\{1, ..., n\}^{(d)}})$ and we find that $f$ is also injective.
\end{proof}
\begin{corollary}[Question (b)]
    \label{prop:image_phi}
    Let $\bar{f}: \Proj(\extpow^d k^n) \to \Proj^{{n \choose d} - 1}$ be the map $f$ from before modulo $k^*$.
    Then
    \begin{equation*}
        \rho = \bar{f} \circ \phi
    \end{equation*}
    and in particular, we see that $\phi(Gr(d, n))$ is a projective variety and isomorphic to $\rho(\Gr(d, n))$.
\end{corollary}
\begin{proposition}[Question (c)]
    The map $\phi$ is injective.
\end{proposition}
\begin{proof}
    Consider two $d$-dimensional subspaces $U, W$ of $k^n$ with $\phi(U) = \phi(W)$.
    Let $u_1, ..., u_l$ be a basis of $U \cap W$ and extend it to bases $u_1, ..., u_d$ of $U$ and $u_1, ..., u_l, w_{l + 1}, ..., w_d$ of $W$.
    As $\phi(U) = \phi(W)$, we can assume that the $u_i, w_i$ are scaled such that
    \begin{align*}
        0 =& (u_1 \wedge ... \wedge u_d) - (u_1 \wedge ... \wedge u_l \wedge w_{l + 1} \wedge ... \wedge w_d) \\
        =& u_1 \wedge ... \wedge u_l \wedge \bigl( (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) \bigr)
    \end{align*}
    By Lemma~\ref{prop:subspace_closed} we see that
    \begin{equation*}
        u_2 \wedge ... \wedge u_l \wedge \bigl( (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) \bigr) = 0
    \end{equation*}
    as $u_1 \notin \vspan\{u_2, ..., u_d, w_{l + 1}, ..., w_d\}$.
    Inductively, this argument shows that for all $2 \leq j \leq l + 1$
    \begin{equation*}
        u_j \wedge ... \wedge u_l \wedge (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) = 0
    \end{equation*}
    Hence
    \begin{equation*}
        (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) = 0
    \end{equation*}
    If $l < d$, we can now apply Lemma~\ref{prop:subspace_closed} again to see that
    \begin{equation*}
        u_{l + 1} \in \vspan\{ u_{l + 2}, ..., u_d, w_{l + 1}, ..., w_d \}
    \end{equation*}
    as $u_{l + 2} \wedge ... \wedge u_d \neq 0$ by Lemma~\ref{prop:extpow_zero_iff_independent}.
    However, this contradicts the linear independence of $u_{l + 1}, ..., u_d, w_{l + 1}, ..., w_d$.
    Hence it must be $l = d$ and so $U = W$.
\end{proof}

@@

In particular, we focus on the case $d = 2$, i.e. examine the variety $\Gr(2, V)$ for different finite-dimensional $V$.
To use our standard methods of Algebraic Geometry, we first introduce coordinates on $\Proj(\extpow^d k^n)$.

@@

    Note that in the proof of Lemma~\ref{prop:basis_product_independence} it was shown that $v_{i_1} \wedge ... \wedge v_{i_d}$ for $i_1 < ... < i_d$ is a basis of $\extpow^d k^n$ if $v_1, ..., v_n$ is a basis of $V$.

@@

        [\omega] \in \mathrm{im}\phi \ \Leftrightarrow \ \omega \wedge \omega = 0

@@

    We find that

@@

@@

    Then for an ideal $I \leq R$ have that the list of all monomials $x_0^{\alpha_0}, ..., x_n^{\alpha_n} \notin \mathrm{lt}(I)$ not contained in $\mathrm{lt}(I)$ are a $k$-vector space basis of $R/I$.

@@

    Consider an arbitrary element $F$ of $I$, given by homogeneous polynomials $f_{i, j, u, v} \in R$ via
    \begin{equation*}
        F = \sum_{i < j < u < v} f_{i, j, u, v} \ (x_{i, v} x_{j, u} - x_{i, u} x_{j, v} + x_{i, j} x_{u, v})
    \end{equation*}
    We want to show that $\mathrm{lt}(F) \in J$.

@@

    So consider now the second case, i.e. $\mathrm{lt}(F) = \epsilon \ x_{i, u} \ x_{j, v} \ f_{i, j, u, v}$.
    Since $x_{i, v} \ x_{j, u} \ f_{i, j, u, v} \succ x_{i, u} \ x_{j, v} \ f_{i, j, u, v}$, we see that the term $x_{i, v} \ x_{j, u} \ f_{i, j, u, v}$ cannot occur in $F$, i.e. must ``cancel out''.
    Hence the monomial $\epsilon \ x_{i, v} \ x_{j, u} \ f_{i, j, u, v}$ has a nonzero coefficient in
    \begin{equation*}
        F - f_{i, j, u, v} \ x_{i, v} \ x_{j, u} = \sum_{\substack{a < b < c < d\\(a, b, c, d) \neq (i, j, u, v)}} f_{a, b, c, d} \ (x_{a, d} x_{b, c} - x_{a, c} x_{b, d} + x_{a, b} x_{c, d})
    \end{equation*}
    and so for $(a, b, c, d) \neq (i, j, u, v), \epsilon' \in k^*$ have that
    \begin{align*}
        f_{i, j, u, v} \ x_{i, v} \ x_{j, u} &= \epsilon' f_{a, b, c, d} \ x_{a, d} \ x_{b, c} \quad \text{or}\\
        f_{i, j, u, v} \ x_{i, v} \ x_{j, u} &= \epsilon' f_{a, b, c, d} \ x_{a, c} \ x_{b, d} \quad \text{or}\\
        f_{i, j, u, v} \ x_{i, v} \ x_{j, u} &= \epsilon' f_{a, b, c, d} \ x_{a, b} \ x_{c, d}
    \end{align*}
    However, the second and third case imply that $f_{a, b, c, d} \ x_{a, d} \ x_{b, c} \succ f_{i, j, u, v} \ x_{i, v} \ x_{j, u}$.
    Hence, the ``new'' monomial $f_{a, b, c, d} \ x_{a, d} \ x_{b, c}$ also has to ``cancel out'' in the sum representation of $F$, as it is greater than $\mathrm{lt}(F) = \epsilon x_{i, u} \ x_{j, v} \ f_{i, j, u, v}$ in the order $\preceq$.
    So applying the whole argument inductively (induction on the number of monomials $\succ f_{i, j, u, v} \ x_{i, v} \ x_{j, u}$ that occur in any of the polynomials we work with), we end up in the first case
    \footnote{There is a small argument missing here, namely that we apply the next argument on each step of the induction, to show the claim for $f_{i, j, u, v} \ x_{i, v} \ x_{j, u}$. However, it should be easy to see that this is possible.}.
